---
title: "data analysis 4th August"
format: html
editor: visual
---

# Overview of the scipt:
# the upper half of my script combines all event tables (named xxx_unfilered.csv) output by python into 1 big event table
# then I assigned new column noise: yes/no, based on my previously analyzed results (to select noise events)
# I also added data entry row just to keep track of all raw detected events
# the bottom half of my script split back all event tables into smaller individual recording
# I did this because my existing R studio scripts to test hypothesis are different for mechanical stimualtor/thermal stimulator/ 4 stim files
# because they have different sweep number, recording length (time), timing of when the stimulus was applied
# and my existing script also works on a folder containing individual csv instead of a big one
# I had function to read individual csv inside a loop, too troublesome to change

# my situation/why I did these stuff:
# I could have keep the raw small csv, then append the new column of data entry row, and event_id row in my folder using loop
# but I did not know how to, and I thought uploading 1 big event table was more organized, therefore I combined stuff tgt
# plus, 1 big event table was better for noise exclusion purpose since I trained my classifier using all recording 
# but then reached size limit unexpectedely
# the script is still useful, since I have event_id, can use to plot indivudal event to inspect noise vs non noise
# can also sort csv files into correct folder (since I already have my python script to sort abf files before event detection, it is easier for me to adopt my sorting script if I work on a folder of small csv, instead of writing a new script to sort and split the big csv into multiple csv of correct folder location (mechanical stimualtor/thermal/ 4stim)


```{r}
library(readr)
library(dplyr)
library(stringr) # not yet cited! rmb to add

# obtain the list of files path inside my event tables folder
files <- list.files(
  path = "event_tables", 
  pattern = "_unfiltered", 
  full.names = TRUE
)

files

# purpose: read every csv event table and combine all csv into 1 big dataframe called all_files
# map_df means put the list of files (variable files) as input, and apply the function onto each element
all_files <- purrr::map_df(.x = files, function (individual_event_table){
  file_name <- individual_event_table |>   # obtain the basename (without the folder name, only file name), store as variable
    basename()
  
  table <- read_csv(individual_event_table) # read the csv table and store as variable table
  table <- table |>             # create a new column called file_name,and update our variable table
    mutate(file_name = file_name)
  }
  )

# remove extension .csv
all_files <- all_files %>%
  mutate(
    file_no_ext = str_replace(file_name, "\\.csv$", ""), # \\ is the escape character to type  dot
    # the sign $ means to grab the .csv only if this string appears at the last of the current string 
    file_prefix = str_replace(file_no_ext, "_unfiltered", ""),
    event_number_padded = sprintf("%05d", `Event Number`), # make event number become 5 digits
    event_id = paste0(file_prefix, "_ev", event_number_padded, "_rec", `Record`)
  )

all_files <- all_files %>%
  select(-file_name, -file_no_ext, -event_number_padded)


# create a new column and assume every event is real event (not noise)
all_files <- all_files |>
  mutate(
    noise = "no"
  )


all_files <- all_files %>%
  mutate(event_entry_number = dplyr::row_number())


# read the noise table of event that were flagged as noise previously by ML model and passed my inspection



noise_events <- read_csv("C:/Users/silic/Desktop/master_project_updated_pipeline_backup/noise_labeling/events_to_label/other_noise/noise.csv",
                   col_names = TRUE)
View(noise_events)


all_files <- all_files %>%
  mutate(
    noise = if_else(event_id %in% noise_events$event_id, "yes", "no")
  )


View(all_files)

# save the big event table that has the noise column (of yes/no)
write_csv(all_files, "all_events_with_noise.csv")
# 508758 rows

all_files_no_noise <- all_files %>%
  filter(noise == "no")

# save the big event table that has noise removed
write_csv(all_files_no_noise, "all_events_no_noise.csv")
# 505516 rows


```


```{r}
library(dplyr)
library(stringr)

# Load big event table
events <- read.csv("C:/Users/silic/Downloads/bitbucket backup/all_events_no_noise.csv")

View(events)

# split big dataframe into list of small event tables 
split_list <- split(events, events$file_prefix)
split_list # why is there only 471 elements?

# length(unique(events$file_prefix))

output_folder <- "sorted_events"
dir.create(output_folder, showWarnings = FALSE)

for (recording in names(split_list)) {
  out_path <- file.path(output_folder, paste0(recording, "_events.csv"))
  write.csv(split_list[[recording]], out_path, row.names = FALSE)
  message("Saved: ", out_path)
}

```

